Dirac neutrino mass generation from Majorana messenger

### 2019-08-01 draft.tex
hjj

\begin{abstract}

We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop. This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

\section{Introduction}
\label{sec:intro}

The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the effective
number of light neutrinos, $N_{\text{eff}}$, until 6. 
To be compatible with the current cosmological restrictions on
$N_{\text{eff}}$, only the  ps w l therm
To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked. For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}. The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}. In this
work we want to explore the possibility to build a simple model with Dirac neutrino
masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.

In models for Dirac neutrinos with some explanation for the smallness of
their masses, usually an adhoc discrete symmetry is invoked to forbid
the SM induced terms of Dirac at tree level and Majorana terms,
and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
In recent works, using symmetry ($B-L$) to forbid these terms without resorting
to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
In these cases, it is necessary to introduce new scalars and new Dirac or 
vector-like fermions, that are required to close the loop.

Another evidence that SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM). The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}. We will make use of the scotogenic model~\cite{Ma:2006km}. In scotogenic model the neutrino masses and the DM have common explanation. The neutrino masses are generated by one-loop effects, where the candidates for DM are mediators in the loop.

>>>>

\begin{abstract}    
We propose a model for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop. This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

\section{Introduction}
\label{sec:intro}
%Dirac or Majorana

The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed.
%Dirac case
If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos,
%with cosmology implications
which can increase the effective number of
light neutrinos, $N_{\text{eff}}$, until 6. Therefore, to be compatible with the
current cosmological restrictions on $N_{\text{eff}}$, the interactions
of the extra right-handed neutrinos with the primordial plasma must be
highly suppressed.

%Smallness of neutrinos for both Dirac and Majorana
On the other hand, To give small masses to at least two Majorana or
Dirac neutrinos, as required to explain the neutrino oscillation
experiments~\cite{Ahmad:2002jz, Fukuda:1998mi},
%focus in seesaw type I
the seesaw mechanism
with heavy fermions is usually invoked.
%tree-level case
For the tree-level type-I
seesaw we can have either light Majorana neutrinos with heavy Majorana
mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia}
or light Dirac neutrinos with heavy Dirac
mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
%one-loop case
The
radiative type-I seesaw includes both~\cite{} possibilities~\cite{},
%new possibility in radiative case
but now it is also possible to have light Majorana neutrinos with

heavy Dirac mediators~\cite{}.
%New in this work
In this work we want to explore the
possibility to build a simple Dirac radiative type-I seesaw  model with 
heavy Majorana mediators.
%Old idea but first realized here
It is worth noticing that this idea have
been already illustrated in an extension of the minimal supersymmetric
standard model~\cite{Demir:2007dt} but without show any explicit
solution.

%Features of the new propossed solution
In general, solutions for light Dirac neutrino masses require a continous symmetry to guarantee their Diracness. This symmetry is usally identified as the $\operatorname{U}(1)_{B-L}$. In models for light Dirac neutrinos, with some explanation for the smallness of
their masses, usually  adhoc discrete symmetries are invoked to forbbid
tree level Dirac or Majorana mass terms for the light right-handed neutrinos~\cite{Han:2018zcn,Wang:2017mcy}.
%tree-level without adhoc symmetries
The tree-level Dirac type-I seesaw with
proper choices for the $\operatorname{U}(1)_{B-L}$ charges have been shown to be consistent without require extra ad-hoc discrette symmetries~\cite{}.
%one-loop 
In recent works, it has been shown that even at one-loop it is possible to have  $\operatorname{U}(1)_{B-L}$ as the only extra symmetry beyond the SM~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}\footnote{
%extra-loops
  For extensions with only extra scalars, solutions have been found with two and three loops}.
%conexion with dark matter
In this radiative cases, as a bonus,  the new scalars and fermions circulating the loop, can be dark matter candidates with the stability of the ligthest particle guarantee by the  very same continous symmetry.
% remark
We focus here in solutions for the radiative Dirac type-I seesaw, with
only an extra symmetry responsible for the Diracness of the light neutrinos, the absence of any tree-level contribution and the existence of a dark sector constituyed by the particles circulating the loop.

%conexion with DM
In fact, another evidence that the SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM). The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}. We will make use of the scotogenic model~\cite{Ma:2006km}. In scotogenic model the neutrino masses and the DM have common explanation. The neutrino masses are generated by one-loop effects, where the candidates for DM are mediators in the loop.
